---
title: "Day 5 morning session"
format: html
editor: visual
execute:
  warning: false
---


```{r}
#| warning: false
#| message: false 

# load libraries ----
library(tidyverse)
# the hash pipe I added at the top makes it so that warning that usually show up when you render the document won't be there 
```


## Star wars data package 
- use the head(), tail(), dim(), and dplyr::starwars  functions to explore data 
```{r}
#| include: false 
# this command above means that this code chunk will not appear in the rendered document 
# data exploration using starwars ----
head(starwars)

tail(starwars)

dim(starwars)

dplyr::starwars
```

- Create a scatter plot of character `mass` (y -axis) and `height` (x-axis)
- Update the color of the points so that color changes based on the value of 'mass'
```{r}
#| warning: false 
#| echo: false
# this execution function allows the code and warnings to be hidden 
ggplot(data = starwars, aes(x= height, y = mass, color = mass))+
  geom_point() +
  labs(x = "Height(cm)",
       y = "Mass (kg)",
       title = "Size variables of Star Wars characters")
```


- Create a histogram of character heights
- Update the fill color (`fill`) to purple and the outside border line (`color`) of each histogram bin to orange 
- Update the axis labels 
- Update your code options so that only your code and output graph appear in the rendered doc 

```{r}
#| fig-cap: "This is my figure caption"
#| fig-alt: "This is some alt text, helpful to explain an image for the visually impaired"
# histogram of character heights ----
ggplot(data = starwars, aes(x = height))+
  geom_histogram(color = "orange", fill = "purple")+
  labs(x = "Height (cm)",
       y = "Count",
       title = "Height frequencies of Star Wars characters")
```

`df$col_name` This is how you grab a single column 
```{r}
# looking at the mean of character heights ----
sw_height_mean <- round(x = mean(starwars$height, na.rm = TRUE),
                        digits =3)
#na.rm removes the NAs from the column. The default is FALSE, meaning it won't remove the NAs before taking the mean
```

The mean height of all star wars characters is `r sw_height_mean`



